Continuous Generalization of Buildings \protect\\ by Growing and Merging

### 2017-08-11 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
writing the paper

\section{Method}

@@

\subsection{Simplification}
we use a buffer-based method, similar to \textcite{Damen2008,Meijers2016}, to 
simplify our grown buildings.

We tried simplifying using Douglas--Peucker algorithm \parencite{Douglas1973}, 
but we hoped to remove more points. We found that the Imai--Iri 
algorithm \parencite{ImaiIri1988} fit our needs well. Although a version with a 
lower running time exists \parencite[see][]{Chan1992}, we implemented the basic 
version.

@@

We add three more constraints for a shortcut to be valid
when we use the Imai--Iri algorithm. 
That is, 
a shortcut is not allowed to intersect the boundary of the original building, 
is not allowed to intersect the boundary of the grown building, 
and must be inside the grown building.
For the first constraint, 
if a shortcut intersects the boundary of the original building, 
we will need to shrink the building, which we do not want.
For the second and the third constraints,
if a shortcut is outside the grown building,
we are not able to arrive at the shortcut by growing.

@@

\section{Section Title}
\label{sec:AStarAlgorithm}

@@

Because of our aggregation with skeletons and original 
buildings, we may have too many details in the intermediate 
results.

Some buildings are too small to be eroded. We have to generate 
squares or MBR?

@@

One can also discuss about our growing speed.

@@

Ideally, for a rectangle, the ratio of width to height should be kept.

The closest place of two buildings before enlarging is not necessarily the same 
as the closest place after enlarging.

>>>>

\section{Methodology}

@@

\subsection{Simplification}
We use an offset-based method, similar to \textcite{Damen2008,Meijers2016}, to 
simplify our grown buildings. We first dilate the grown buildings to remove 
pits, and then erode the results to remove spikes.

After carrying out the offset-based method, we simplify the grown buildings 
We tried simplifying using Douglas--Peucker algorithm \parencite{Douglas1973}, 
but we hoped to remove more points. We found that the Imai--Iri 
algorithm \parencite{ImaiIri1988} fit our needs well. Although a version with a 
lower running time exists \parencite[see][]{Chan1992}, we implemented the basic 
version.

@@

\todo[inline]{more details in the below paragraph?}
We add two more constraints for a shortcut to be valid
when we use the Imai--Iri algorithm. 
The first one is that
a shortcut must be completely inside the grown building.
If a shortcut is outside,
we are not able to arrive at the shortcut by growing.
The second constraint is that a shortcut is not allowed to intersect the 
boundary of the original building.
If a shortcut does intersect, 
we will need to shrink the building instead of growing. Of course, we do not 
want to shrink.

@@

\section{Case Study}
\label{sec:CaseStudy}
We have implemented our method based on C\# (Microsoft Visual 
Studio 
2015) and ArcObjects SDK \revise{for the Microsoft .Net Framework}{}10.2. 
We ran our case study under 64-bit 
Windows 7 on a 3.3 GHz dual core CPU with 8 GB RAM.
%As ArcObjects SDK for the Microsoft .Net Framework 10.2 can 
%only  run under a 32-bit platform, we set a Post-build 
%event\footnote{The details of the setting can be found at 	
%\url{http://stackoverflow.com/questions/2597790/can-i-set-largeaddressaware-from-within-visual-studio}.},
%in Microsoft Visual Studio 2012
%so that we managed to use up to 3GM of RAM.
We measured processing time by the built-in C\# class 
\emph{Stopwatch}.
We tested our method on a dataset from the German topographic 
database ATKIS DLM 50. The dataset represents the place 
``Buchholz in der Nordheide'' at scale $1:50{,}000$. Our start 
map is the map after the collapse of areas by \citet[pp. 
61--66]{haunert2008f}, which has $5{,}537$ polygons. Our goal 
map was generalized from the start map by 
\citet{haunertwolff2010b} setting the scale at $1:250{,}000$ 
(see Fig.~\ref{fig:Data}). The goal map has $734$ polygons, 
which means that \revise{we have}{there are $N=734$} regions.

@@

@@

@@

Eventually, our result is a set of settlement boundaries. An interesting 
problem is to compare our method with \textcite{Chaudhry2008}.
